\Title

### 2016-02-23 manuscript/manuscript.tex
Add model information in crust1 synthetic

In this test, we simulate the anomalous Moho of South America
using the Moho depth of the CRUST1.0 model
\citep[][ Fig.~\ref{fig:crust1-data}a]{laske2013}.
The Normal Earth Moho is $z_{ref} = 30\ km$ and
the density-contrast is $\Delta\rho = 350\ kg/m^3$.
We forward model the gravitational attraction of the anomalous Moho
on a regular grid of $N_{lat} \times N_{lon} = 159 \times 119$ points
(a total of 18921 observations) at a constant height of 50 km.
We contaminate the synthetic data with normally distributed pseudo-random noise
with zero mean and 5 mGal standard deviation (Fig.~\ref{fig:crust1-data}b).

The cross-validation procedure to determine $\Delta\rho$ and $z_{ref}$
requires knowledge of the Moho depth at certain points,
usually from seismic experiments.
Thus, we must also generate synthetic seismic data about the Moho depth.
We produce such data by interpolating the Moho depth shown in
Fig.~\ref{fig:crust1-data}a on the same geographic coordinates as the
data from \citet{assumpcao2012}.
The resulting synthetic seismic data is shown in Fig.~\ref{fig:crust1-data}c.

>>>>

In this test, we simulate the anomalous Moho of South America
using Moho depth information extracted from the CRUST1.0 model
\citep{laske2013}.
We construct a model with
$M_{lat} \times M_{lon} = 80 \times 60$ tesseroids, 4800 in total,
using the Moho depths shown in Fig.~\ref{fig:crust1-data}a.
In our model, the Normal Earth Moho is $z_{ref} = 30\ km$ and
the density-contrast is $\Delta\rho = 350\ kg/m^3$.
We forward model the gravitational attraction of the anomalous Moho
on a regular grid of $N_{lat} \times N_{lon} = 159 \times 119$ points
(a total of 18921 observations) at a constant height of 50 km.
We contaminate the synthetic data with normally distributed pseudo-random noise
with zero mean and 5 mGal standard deviation (Fig.~\ref{fig:crust1-data}b).

The cross-validation procedure to determine $\Delta\rho$ and $z_{ref}$
requires knowledge of the Moho depth at certain points
($\mathbf{z}_s^o$ in Eq.~\ref{eq:msehyper}),
usually from seismic experiments.
Thus, we must also generate synthetic seismic data about the Moho depth.
We produce such data by interpolating the Moho depth shown in
Fig.~\ref{fig:crust1-data}a on the same geographic coordinates as the
data from \citet{assumpcao2012}.
The resulting synthetic seismic data is shown in Fig.~\ref{fig:crust1-data}c.

We ran cross-validation to estimate an optimal regularization parameter ($\mu$)
by separating the synthetic data into training and testing data sets
(Fig.~\ref{fig:grid_separation}).
The training data set is a regular grid
with half the grid spacing of the original data
($N_{lat} \times N_{lon} = 159 \times $)
